PrepCAISOData

### 2014-12-23 CAData/CAISO/LoadData.Rmd
Basic model in but there is an AR problem.

>>>>

```{r}
library(lmtest)
dwtest(Base)

```
There is autocorrelation

```{r}
dwtest(lm(Actual~Forecast+traffic,data=WTrends))

dwtest(lm(Actual~Forecast+restaurants,data=WTrends))

dwtest(lm(Actual~Forecast+gas,data=WTrends))

dwtest(lm(Actual~Forecast+movies,data=WTrends))

Autocorreleation in everything.

Moving to a lag formulation like in the day ahead model.
Add the lags to dataset
```{r}

CopyWTrends<-WTrends
library(sqldf)

WLags<-sqldf("select WTrends.*, CopyWTrends.Actual as LActual, CopyWTrends.Forecast LForecast, CopyWTrends.weather as LWeather, CopyWTrends.traffic as LTraffic,CopyWTrends.gas as LGas, CopyWTrends.movies as LMovies from WTrends, CopyWTrends  where WTrends.Hour=CopyWTrends.Hour and WTrends.Date=(CopyWTrends.Date-7) ")

summary(WLags)
```

Base<-lm(Actual~-1 +(LActual+weather+LWeather)*Hour, data=WLags)

summary(Base)
dwtest(Base)
```

Buahhahah  It works better for the peak hours.  There is still AR

```{r}
library(nlme)
#ARbyHourDay<-gls(Actual~-1 +(LActual+weather+LWeather), data=WLags,corAR1(form=~1),na.action=na.omit)

```
Gona need a bigger boat.  3.9Gb.
